Supplement to ``{\mytitle}''

### 2023-09-06 si/ReplicateLee20.Rnw
Modified makefile because sed is not the same for mac and linux

\begin{figure}[!h]
<<plotModel2Rep, cache=TRUE, echo=FALSE, fig.width=6.5, fig.height=4.5>>=
gg_epi <- projections %>%
  filter(date < as.Date("03-01-2014", format = '%m-%d-%Y')) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = ReportedAll), col = 'black', linetype = 'dashed') +
  geom_line(aes(y = Ctotal), col = 'red', size = 1) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 30000), breaks = seq(0, 30000, 5000)) +
  theme(axis.title.x = element_blank()) +
  ylab("Reported number of cases")

gg_end <- projections %>%
  filter(date >= as.Date("03-01-2014", format = '%m-%d-%Y')) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = ReportedAll), col = 'black', linetype = 'dashed') +
  geom_line(aes(y = Ctotal), col = 'red', size = 1) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 7000), breaks = seq(0, 7000, 1000)) +
  theme(axis.title.x = element_blank()) +
  ylab("Reported number of cases") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y")

>>>>

\begin{figure}[!h]
<<plotModel2Rep, cache=TRUE, echo=FALSE, fig.width=6.5, fig.height=4.5>>=
gg_epi <- projections %>%
  filter(date < as.Date("03-01-2014", format = '%m-%d-%Y')) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = ReportedAll), col = 'black', linetype = 'dashed') +
  geom_line(aes(y = Ctotal), col = 'red', linewidth = 1) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 30000), breaks = seq(0, 30000, 5000)) +
  theme(axis.title.x = element_blank()) +
  ylab("Reported number of cases")

gg_end <- projections %>%
  filter(date >= as.Date("03-01-2014", format = '%m-%d-%Y')) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = ReportedAll), col = 'black', linetype = 'dashed') +
  geom_line(aes(y = Ctotal), col = 'red', linewidth = 1) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 7000), breaks = seq(0, 7000, 1000)) +
  theme(axis.title.x = element_blank()) +
  ylab("Reported number of cases") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y")
